Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Conclusion.tex

Moving this work towards generating a fully verified MSI implementation
requires a number of small steps. First, the simple transliteration of
descriptions between Bluespec and Coq, must be done in a mechanical way.
Second, the compilation of Bluespec to hardware is unverified; to fully trust
the implementation the Bluespec compiler must be verified. Some initial work on
this has already been done~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must
extend our notion of correctness to provide some guarantee of
liveness and fairness in handling of requests from processors. We have
initial Coq-based proofs that with finite buffers a local fairness in
transaction our protocol will have this property, but more work is needed to
fully resolve this venture.

>>>>

Moving this work towards generating a fully verified MSI implementation
requires a number of small steps. First, the simple transliteration of
descriptions between Bluespec and Coq, must be done in a mechanical way.
Second, the compilation of Bluespec to hardware is unverified; to fully trust
the implementation the Bluespec compiler must be verified. Some initial work on
this has already been done~\cite{TDBLP:conf/cav/BraibantC13}. Finally, we must
extend our notion of correctness to provide some guarantee of
liveness and fairness in handling of requests from processors. We have
initial Coq-based proofs that with finite buffers a local fairness in
transaction our protocol will have this property, but more work is needed.
